\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach

### 2021-08-10 presentationESSLLI21/presentationESSLLI.Rmd
Adds all
Updates
Adds current

### Cosine-based bias: basic intuition

@@

- feminine occupations: "homemaker", "nurse", "receptionist", "librarian", etc.

- masculine occupations:  "maestro",  "captain", "architect", "boss", etc.

@@

   \begin{itemize}
   \item Most intervals overlap with control groups
   \item Often not too much diffence between associated and different
   \end{itemize}
   \end{minipage}
\end{figure}

>>>>

### The basic intuition

@@

- "feminine" occupations: "homemaker", "nurse", "receptionist", "librarian", etc.

- "masculine" occupations:  "maestro",  "captain", "architect", "boss", etc.

@@

   \begin{itemize}
   \item Most intervals overlap with control groups
   \item Often not too much difference between associated and different
   \end{itemize}
   \end{minipage}
\end{figure}
